\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{physics}
\usepackage[mathscr]{euscript}
\let\euscr\mathscr \let\mathscr\relax
\usepackage[scr]{rsfso}
\newcommand{\powerset}{\raisebox{.15\baselineskip}{\Large\ensuremath{\wp}}}


\usepackage{mathtools}


\numberwithin{equation}{section}

\newcommand{\vah}[1]{\va{\hat{#1}}}
\newcommand{\vbh}[1]{\vb{\hat{#1}}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\FT}{\mathcal{F}}
\newcommand\perm[2][^n]{\prescript{#1\mkern-2.5mu}{}P_{#2}}
\newcommand\comb[2][^n]{\prescript{#1\mkern-0.5mu}{}C_{#2}}

\DeclareMathOperator{\spn}{span}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\title{PHYS 104 Homework 2}
\author{Siyu Chen}
\date{Summer 2023}

\begin{document}

\maketitle

\section{Thornton and Marion 7.3.}

\paragraph{A sphere of radius $\rho$ is constrained to roll without slipping on the lower half of the inner surface of a hollow cylinder of inside radius $R$. Determine the Lagrangian function, the equation of constraint, and Lagrange’s equations of motion. Find the frequency of small oscillations. \\}

\section{Thornton and Marion 7.5.}

\paragraph{Consider a vertical plane in a constant gravitational field. Let the origin of a coordinate system be located at some point in this plane. A particle of mass $m$ moves in the vertical plane under the influence of gravity and under the influence of an additional force $f = -A r^{\alpha-1}$ directed towards the origin. Chose appropriate generalized coordinates and find the Lagrangian equations of motion. Is the angular momentum about the origin conserved? Explain. \\}

\section{Thornton and Marion 7.37.}

\paragraph{Use the method of Lagrange multipliers to find the tensions in both strings of the double Atwood machine of example 7.8 (The example from lecture 4 in class). \\}

\section{Thornton and Marion 7.39.}

\paragraph{An extremely limber rope of uniform mass density, mass $m$, and total length $b$ lies on a table with a length $z$ hanging over the edge of the table. Only gravity acts on the rope. Find Lagrange’s equation of motion.\\}

\section{Thornton and Marion 7.41.}

\paragraph{A pendulum of length $b$ and mass bob $m$ is oscillating at small angles when the length of the pendulum string is shortened at a velocity of $\alpha$. Find Lagrange’s equations of motion. \\}

\end{document}
